---
title: "ANOVA_unique_vs_shared"
author: "Kai Shaman"
date: "12-09-2023"
note: "ANOVAs comparing numbers of Unique and Shared Neurons between conditions"
---
# ALL AREAS
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# LOAD PACKAGES
library(grid)
library(rstatix)
library(ggplot2)
library(data.table)
library(ggpubr)
library(Rmisc)
library(gridExtra)
library(ggsignif)
options(scipen = 999)
```

```{r, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# LOAD DATAFRAMES WITH Percent_shared MEASURES FOR EACH AREA FOR PLOTTING AND DATAFRAMES WITH Percent_shared MEASURES FOR WHOLE NETWORKS (ACROSS ALL AREAS) FOR ANOVA
directory <- file.path(getwd(), "ANOVA") # get path to directory with files

list_data <- list.files(path=directory, pattern="shared_neurons", all.files=TRUE,full.names=TRUE) 
data1 <- read.csv(list_data[[1]])
data1$Condition <- "English"
data2 <- read.csv(list_data[[2]])
data2$Condition <- "Greek"
data3 <- read.csv(list_data[[3]])
data3$Condition <- "Pre-Language"

data_all <- rbind(data1, data2, data3)
data_all$Neuron_Type[data_all$Neuron_Type == 'UniqueN'] <- 'Unique'
data_all$Neuron_Type[data_all$Neuron_Type == 'OverlapN'] <- 'Shared'
data_all_sum <- ddply(data_all, c("Network", "Condition", "Neuron_Type", "Color"),numcolwise(sum), na.rm=TRUE)
pre_en_all <- data_all_sum %>%  filter(Condition %in% c("Pre-Language","English"))
pre_gr_all <- data_all_sum %>%  filter(Condition %in% c("Pre-Language","Greek"))

data_hub <- data_all %>% filter(Area %in% c("AT","PFL","PB","PFI"))
data_hub_sum <- ddply(data_hub, c("Network", "Condition", "Neuron_Type", "Color"),numcolwise(sum), na.rm=TRUE)
pre_en_hub <- data_hub_sum %>%  filter(Condition %in% c("Pre-Language","English"))
pre_gr_hub <- data_hub_sum %>%  filter(Condition %in% c("Pre-Language","Greek"))

data_visual <- data_all %>% filter(Area %in% c("V1","AT","TO"))
data_visual_sum <- ddply(data_visual, c("Network", "Condition", "Neuron_Type", "Color"),numcolwise(sum), na.rm=TRUE)
pre_en_visual <- data_visual_sum %>%  filter(Condition %in% c("Pre-Language","English"))
pre_gr_visual <- data_visual_sum %>%  filter(Condition %in% c("Pre-Language","Greek"))

data_at <- data_all %>% filter(Area %in% c("AT"))
data_at_sum <- ddply(data_at, c("Network", "Condition", "Neuron_Type", "Color"),numcolwise(sum), na.rm=TRUE)
pre_en_at <- data_at_sum %>%  filter(Condition %in% c("Pre-Language","English"))
pre_gr_at <- data_at_sum %>%  filter(Condition %in% c("Pre-Language","Greek"))

data_to <- data_all %>% filter(Area %in% c("TO"))
data_to_sum <- ddply(data_to, c("Network", "Condition", "Neuron_Type", "Color"),numcolwise(sum), na.rm=TRUE)
pre_en_to <- data_to_sum %>%  filter(Condition %in% c("Pre-Language","English"))
pre_gr_to <- data_to_sum %>%  filter(Condition %in% c("Pre-Language","Greek"))
```

# ALL AREAS
# PRE-LANGUAGE VS. ENGLISH (ALL AREAS): ANOVA
```{r, echo=FALSE, message=FALSE, warning=FALSE}
anova_pre_en_all <- anova_test(data = pre_en_all, dv = AbsoluteNo, wid = Network, within = c(Condition,Neuron_Type,Color))
anova_pre_en_all <- as.data.frame(get_anova_table(anova_pre_en_all, correction = "GG"))
write.csv(anova_pre_en_all, file=file.path("ANOVA",paste0("all_pre_en_anova.csv")))
anova_pre_en_all
```
# PRE-LANGUAGE VS. ENGLISH (ALL AREAS): POST-HOC
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pairwise_all_pre_en <- pre_en_all %>% group_by(Neuron_Type, Color) %>% pairwise_t_test(AbsoluteNo ~ Condition, paired = TRUE)
write.csv(pairwise_all_pre_en, file=file.path("ANOVA",paste0("all_pre_en_pairwise.csv")))
pairwise_all_pre_en
```
# PRE-LANGUAGE VS. GREEK (ALL AREAS): ANOVA
```{r, echo=FALSE, message=FALSE, warning=FALSE}
anova_pre_gr_all <- anova_test(data = pre_gr_all, dv = AbsoluteNo, wid = Network, within = c(Condition,Neuron_Type,Color))
anova_pre_gr_all <- as.data.frame(get_anova_table(anova_pre_gr_all, correction = "GG"))
write.csv(anova_pre_gr_all, file=file.path("ANOVA",paste0("all_pre_gr_anova.csv")))
anova_pre_gr_all
```
# PRE-LANGUAGE VS. GREEK (ALL AREAS): POST-HOC
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pairwise_all_pre_gr <- pre_gr_all %>% group_by(Neuron_Type, Color) %>% pairwise_t_test(AbsoluteNo ~ Condition, paired = TRUE)
write.csv(pairwise_all_pre_gr, file=file.path("ANOVA",paste0("all_pre_gr_pairwise.csv")))
pairwise_all_pre_gr
```
# SHARED NEURONS (ALL AREAS): BOXPLOT
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pre_en_all_shared <- pre_en_all %>% filter(Neuron_Type %in% c("Shared"))
pre_gr_all_shared <- pre_gr_all %>% filter(Neuron_Type %in% c("Shared"))
ansh_sum_st1_en <- summarySE(pre_en_all_shared, measurevar="AbsoluteNo", groupvars=c("Color","Condition"))
ansh_sum_st1_gr <- summarySE(pre_gr_all_shared, measurevar="AbsoluteNo", groupvars=c("Color","Condition"))

all_ansh_plot_st1_en <- ggplot(ansh_sum_st1_en,aes(x=factor(Condition, level=c("Pre-Language", "English")), color=Color))+ 
  geom_boxplot(aes(middle=AbsoluteNo,lower=AbsoluteNo-se,upper=AbsoluteNo+se,ymin=AbsoluteNo-sd,ymax=AbsoluteNo+sd),stat="identity") +
  scale_color_manual(breaks = c("Blue", "Green"),values=c("blue", "darkgreen")) + ylim(-2, 85) + labs(y="", x ="") +
  stat_pvalue_manual(data = pairwise_all_pre_en[pairwise_all_pre_en$Neuron_Type == 'Shared',], label = "p.adj.signif", xmin = "group1", xmax="group2",y.position = c(85,0), color="Color", tip.length = 0, label.size = 8) +
  ggtitle("All areas (shared)") +
  theme(plot.title = element_text(size = 21, hjust = 0.5), axis.text=element_text(size=18, color ="black"), legend.position="top", legend.key.size = unit(0.7, 'cm'), legend.title = element_text(size=18), legend.text = element_text(size=16))

all_ansh_plot_st1_gr <- ggplot(ansh_sum_st1_gr,aes(x=factor(Condition, level=c("Pre-Language", "Greek")), color=Color))+ 
  geom_boxplot(aes(middle=AbsoluteNo,lower=AbsoluteNo-se,upper=AbsoluteNo+se,ymin=AbsoluteNo-sd,ymax=AbsoluteNo+sd),stat="identity") +
  scale_color_manual(breaks = c("Blue", "Green"),values=c("blue", "darkgreen")) + ylim(-2, 85) + labs(y="", x ="") +
  stat_pvalue_manual(data = pairwise_all_pre_gr[pairwise_all_pre_gr$Neuron_Type == 'Shared',], label = "p.adj.signif", xmin = "group1", xmax="group2",y.position = c(85,0), color="Color", tip.length = 0, label.size = 8) +
  ggtitle("") +
  theme(plot.title = element_text(size = 21, hjust = 0.5), axis.text=element_text(size=18, color ="black"), legend.position="top", legend.key.size = unit(0.7, 'cm'), legend.title = element_text(size=18), legend.text = element_text(size=16))

all_ansh_plot_st1_en_gr <- grid.arrange(all_ansh_plot_st1_en, all_ansh_plot_st1_gr, ncol=2)
ggsave(all_ansh_plot_st1_en_gr, file=file.path("ANOVA",paste0("all_shared_boxplot.png")))
```
# UNIQUE NEURONS (ALL AREAS): BOXPLOT
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pre_en_all_unique <- pre_en_all %>% filter(Neuron_Type %in% c("Unique"))
pre_gr_all_unique <- pre_gr_all %>% filter(Neuron_Type %in% c("Unique"))
anun_sum_st1_en <- summarySE(pre_en_all_unique, measurevar="AbsoluteNo", groupvars=c("Color","Condition"))
anun_sum_st1_gr <- summarySE(pre_gr_all_unique, measurevar="AbsoluteNo", groupvars=c("Color","Condition"))

all_anun_plot_st1_en <- ggplot(anun_sum_st1_en,aes(x=factor(Condition, level=c("Pre-Language", "English")), color=Color))+ 
  geom_boxplot(aes(middle=AbsoluteNo,lower=AbsoluteNo-se,upper=AbsoluteNo+se,ymin=AbsoluteNo-sd,ymax=AbsoluteNo+sd),stat="identity") +
  scale_color_manual(breaks = c("Blue", "Green"),values=c("blue", "darkgreen")) + ylim(-2, 85) + labs(y="", x ="") +
  stat_pvalue_manual(data = pairwise_all_pre_en[pairwise_all_pre_en$Neuron_Type == 'Unique',], label = "p.adj.signif", xmin = "group1", xmax="group2",y.position = c(82,0), color="Color", tip.length = 0, label.size = 8) +
  ggtitle("All areas (unique)") +
  theme(plot.title = element_text(size = 21, hjust = 0.5), axis.text=element_text(size=18, color ="black"), legend.position="top", legend.key.size = unit(0.7, 'cm'), legend.title = element_text(size=18), legend.text = element_text(size=16))

all_anun_plot_st1_gr <- ggplot(anun_sum_st1_gr,aes(x=factor(Condition, level=c("Pre-Language", "Greek")), color=Color))+ 
  geom_boxplot(aes(middle=AbsoluteNo,lower=AbsoluteNo-se,upper=AbsoluteNo+se,ymin=AbsoluteNo-sd,ymax=AbsoluteNo+sd),stat="identity") +
  scale_color_manual(breaks = c("Blue", "Green"),values=c("blue", "darkgreen")) + ylim(-2, 85) + labs(y="", x ="") +
  stat_pvalue_manual(data = pairwise_all_pre_gr[pairwise_all_pre_gr$Neuron_Type == 'Unique',], label = "p.adj.signif", xmin = "group1", xmax="group2",y.position = c(82,0), color="Color", tip.length = 0, label.size = 8) +
  ggtitle("") +
  theme(plot.title = element_text(size = 21, hjust = 0.5), axis.text=element_text(size=18, color ="black"), legend.position="top", legend.key.size = unit(0.7, 'cm'), legend.title = element_text(size=18), legend.text = element_text(size=16))

all_anun_plot_st1_en_gr <- grid.arrange(all_anun_plot_st1_en, all_anun_plot_st1_gr, ncol=2)
ggsave(all_anun_plot_st1_en_gr, file=file.path("ANOVA",paste0("all_unique_boxplot.png")))
```

# HUB AREAS
# PRE-LANGUAGE VS. ENGLISH (HUB AREAS): ANOVA
```{r, echo=FALSE, message=FALSE, warning=FALSE}
anova_pre_en_hub <- anova_test(data = pre_en_hub, dv = AbsoluteNo, wid = Network, within = c(Condition,Neuron_Type,Color))
anova_pre_en_hub <- as.data.frame(get_anova_table(anova_pre_en_hub, correction = "GG"))
write.csv(anova_pre_en_hub, file=file.path("ANOVA",paste0("hub_pre_en_anova.csv")))
anova_pre_en_hub
```
# PRE-LANGUAGE VS. ENGLISH (HUB AREAS): POST-HOC
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pairwise_hub_pre_en <- pre_en_hub %>% group_by(Neuron_Type, Color) %>% pairwise_t_test(AbsoluteNo ~ Condition, paired = TRUE)
write.csv(pairwise_hub_pre_en, file=file.path("ANOVA",paste0("hub_pre_en_pairwise.csv")))
pairwise_hub_pre_en
```
# PRE-LANGUAGE VS. GREEK (HUB AREAS): ANOVA
```{r, echo=FALSE, message=FALSE, warning=FALSE}
anova_pre_gr_hub <- anova_test(data = pre_gr_hub, dv = AbsoluteNo, wid = Network, within = c(Condition,Neuron_Type,Color))
anova_pre_gr_hub <- as.data.frame(get_anova_table(anova_pre_gr_hub, correction = "GG"))
write.csv(anova_pre_gr_hub, file=file.path("ANOVA",paste0("hub_pre_gr_anova.csv")))
anova_pre_gr_hub
```
# PRE-LANGUAGE VS. GREEK (HUB AREAS): POST-HOC
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pairwise_hub_pre_gr <- pre_gr_hub %>% group_by(Neuron_Type, Color) %>% pairwise_t_test(AbsoluteNo ~ Condition, paired = TRUE)
write.csv(pairwise_hub_pre_gr, file=file.path("ANOVA",paste0("hub_pre_gr_pairwise.csv")))
pairwise_hub_pre_gr
```
# SHARED NEURONS (HUB AREAS): BOXPLOT
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pre_en_hub_shared <- pre_en_hub %>% filter(Neuron_Type %in% c("Shared"))
pre_gr_hub_shared <- pre_gr_hub %>% filter(Neuron_Type %in% c("Shared"))
ansh_sum_st1_en <- summarySE(pre_en_hub_shared, measurevar="AbsoluteNo", groupvars=c("Color","Condition"))
ansh_sum_st1_gr <- summarySE(pre_gr_hub_shared, measurevar="AbsoluteNo", groupvars=c("Color","Condition"))

hub_ansh_plot_st1_en <- ggplot(ansh_sum_st1_en,aes(x=factor(Condition, level=c("Pre-Language", "English")), color=Color))+ 
  geom_boxplot(aes(middle=AbsoluteNo,lower=AbsoluteNo-se,upper=AbsoluteNo+se,ymin=AbsoluteNo-sd,ymax=AbsoluteNo+sd),stat="identity") +
  scale_color_manual(breaks = c("Blue", "Green"),values=c("blue", "darkgreen")) + ylim(-3, 50) + labs(y="", x ="") +
  stat_pvalue_manual(data = pairwise_hub_pre_en[pairwise_hub_pre_en$Neuron_Type == 'Shared',], label = "p.adj.signif", xmin = "group1", xmax="group2",y.position = c(45, -3), color="Color", tip.length = 0, label.size = 8) +
  ggtitle("Hub areas (shared)") +
  theme(plot.title = element_text(size = 21, hjust = 0.5), axis.text=element_text(size=18, color ="black"), legend.position="top", legend.key.size = unit(0.7, 'cm'), legend.title = element_text(size=18), legend.text = element_text(size=16))

hub_ansh_plot_st1_gr <- ggplot(ansh_sum_st1_gr,aes(x=factor(Condition, level=c("Pre-Language", "Greek")), color=Color))+ 
  geom_boxplot(aes(middle=AbsoluteNo,lower=AbsoluteNo-se,upper=AbsoluteNo+se,ymin=AbsoluteNo-sd,ymax=AbsoluteNo+sd),stat="identity") +
  scale_color_manual(breaks = c("Blue", "Green"),values=c("blue", "darkgreen")) + ylim(-3, 50) + labs(y="", x ="") +
  stat_pvalue_manual(data = pairwise_hub_pre_gr[pairwise_hub_pre_gr$Neuron_Type == 'Shared',], label = "p.adj.signif", xmin = "group1", xmax="group2",y.position = c(-3, 35), color="Color", tip.length = 0, label.size = 8) +
  ggtitle("") +
  theme(plot.title = element_text(size = 21, hjust = 0.5), axis.text=element_text(size=18, color ="black"), legend.position="top", legend.key.size = unit(0.7, 'cm'), legend.title = element_text(size=18), legend.text = element_text(size=16))

hub_ansh_plot_st1_en_gr <- grid.arrange(hub_ansh_plot_st1_en, hub_ansh_plot_st1_gr, ncol=2)
ggsave(hub_ansh_plot_st1_en_gr, file=file.path("ANOVA",paste0("hub_shared_boxplot.png")))
```
# UNIQUE NEURONS (HUB AREAS): BOXPLOT
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pre_en_hub_unique <- pre_en_hub %>% filter(Neuron_Type %in% c("Unique"))
pre_gr_hub_unique <- pre_gr_hub %>% filter(Neuron_Type %in% c("Unique"))
anun_sum_st1_en <- summarySE(pre_en_hub_unique, measurevar="AbsoluteNo", groupvars=c("Color","Condition"))
anun_sum_st1_gr <- summarySE(pre_gr_hub_unique, measurevar="AbsoluteNo", groupvars=c("Color","Condition"))

hub_anun_plot_st1_en <- ggplot(anun_sum_st1_en,aes(x=factor(Condition, level=c("Pre-Language", "English")), color=Color))+ 
  geom_boxplot(aes(middle=AbsoluteNo,lower=AbsoluteNo-se,upper=AbsoluteNo+se,ymin=AbsoluteNo-sd,ymax=AbsoluteNo+sd),stat="identity") +
  scale_color_manual(breaks = c("Blue", "Green"),values=c("blue", "darkgreen")) + ylim(-3, 50) + labs(y="", x ="") +
  stat_pvalue_manual(data = pairwise_hub_pre_en[pairwise_hub_pre_en$Neuron_Type == 'Unique',], label = "p.adj.signif", xmin = "group1", xmax="group2",y.position = c(20,-2), color="Color", tip.length = 0, label.size = 8) +
  ggtitle("Hub areas (unique)") +
  theme(plot.title = element_text(size = 21, hjust = 0.5), axis.text=element_text(size=18, color ="black"), legend.position="top", legend.key.size = unit(0.7, 'cm'), legend.title = element_text(size=18), legend.text = element_text(size=16))

hub_anun_plot_st1_gr <- ggplot(anun_sum_st1_gr,aes(x=factor(Condition, level=c("Pre-Language", "Greek")), color=Color))+ 
  geom_boxplot(aes(middle=AbsoluteNo,lower=AbsoluteNo-se,upper=AbsoluteNo+se,ymin=AbsoluteNo-sd,ymax=AbsoluteNo+sd),stat="identity") +
  scale_color_manual(breaks = c("Blue", "Green"),values=c("blue", "darkgreen")) + ylim(-3, 50) + labs(y="", x ="") +
  stat_pvalue_manual(data = pairwise_hub_pre_gr[pairwise_hub_pre_gr$Neuron_Type == 'Unique',], label = "p.adj.signif", xmin = "group1", xmax="group2",y.position = c(35,-2), color="Color", tip.length = 0, label.size = 8) +
  ggtitle("") +
  theme(plot.title = element_text(size = 21, hjust = 0.5), axis.text=element_text(size=18, color ="black"), legend.position="top", legend.key.size = unit(0.7, 'cm'), legend.title = element_text(size=18), legend.text = element_text(size=16))

hub_anun_plot_st1_en_gr <- grid.arrange(hub_anun_plot_st1_en, hub_anun_plot_st1_gr, ncol=2)
ggsave(hub_anun_plot_st1_en_gr, file=file.path("ANOVA",paste0("hub_unique_boxplot.png")))
```

# VISUAL AREAS
# PRE-LANGUAGE VS. ENGLISH (VISUAL AREAS): ANOVA
```{r, echo=FALSE, message=FALSE, warning=FALSE}
anova_pre_en_visual <- anova_test(data = pre_en_visual, dv = AbsoluteNo, wid = Network, within = c(Condition,Neuron_Type,Color))
anova_pre_en_visual <- as.data.frame(get_anova_table(anova_pre_en_visual, correction = "GG"))
write.csv(anova_pre_en_visual, file=file.path("ANOVA",paste0("visual_pre_en_anova.csv")))
anova_pre_en_visual
```
# PRE-LANGUAGE VS. ENGLISH (VISUAL AREAS): POST-HOC
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pairwise_visual_pre_en <- pre_en_visual %>% group_by(Neuron_Type, Color) %>% pairwise_t_test(AbsoluteNo ~ Condition, paired = TRUE)
write.csv(pairwise_visual_pre_en, file=file.path("ANOVA",paste0("visual_pre_en_pairwise.csv")))
pairwise_visual_pre_en
```
# PRE-LANGUAGE VS. GREEK (VISUAL AREAS): ANOVA
```{r, echo=FALSE, message=FALSE, warning=FALSE}
anova_pre_gr_visual <- anova_test(data = pre_gr_visual, dv = AbsoluteNo, wid = Network, within = c(Condition,Neuron_Type,Color))
anova_pre_gr_visual <- as.data.frame(get_anova_table(anova_pre_gr_visual, correction = "GG"))
write.csv(anova_pre_gr_visual, file=file.path("ANOVA",paste0("visual_pre_gr_anova.csv")))
anova_pre_gr_visual
```
# PRE-LANGUAGE VS. GREEK (VISUAL AREAS): POST-HOC
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pairwise_visual_pre_gr <- pre_gr_visual %>% group_by(Neuron_Type, Color) %>% pairwise_t_test(AbsoluteNo ~ Condition, paired = TRUE)
write.csv(pairwise_visual_pre_gr, file=file.path("ANOVA",paste0("visual_pre_gr_pairwise.csv")))
pairwise_visual_pre_gr
```
# SHARED NEURONS (VISUAL AREAS): BOXPLOT
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pre_en_visual_shared <- pre_en_visual %>% filter(Neuron_Type %in% c("Shared"))
pre_gr_visual_shared <- pre_gr_visual %>% filter(Neuron_Type %in% c("Shared"))
ansh_sum_st1_en <- summarySE(pre_en_visual_shared, measurevar="AbsoluteNo", groupvars=c("Color","Condition"))
ansh_sum_st1_gr <- summarySE(pre_gr_visual_shared, measurevar="AbsoluteNo", groupvars=c("Color","Condition"))

visual_ansh_plot_st1_en <- ggplot(ansh_sum_st1_en,aes(x=factor(Condition, level=c("Pre-Language", "English")), color=Color))+ 
  geom_boxplot(aes(middle=AbsoluteNo,lower=AbsoluteNo-se,upper=AbsoluteNo+se,ymin=AbsoluteNo-sd,ymax=AbsoluteNo+sd),stat="identity") +
  scale_color_manual(breaks = c("Blue", "Green"),values=c("blue", "darkgreen")) + ylim(-2, 30) + labs(y="", x ="") +
  stat_pvalue_manual(data = pairwise_visual_pre_en[pairwise_visual_pre_en$Neuron_Type == 'Shared',], label = "p.adj.signif", xmin = "group1", xmax="group2",y.position = c(0,20), color="Color", tip.length = 0, label.size = 8) +
  ggtitle("Visual areas (shared)") +
  theme(plot.title = element_text(size = 21, hjust = 0.5), axis.text=element_text(size=18, color ="black"), legend.position="top", legend.key.size = unit(0.7, 'cm'), legend.title = element_text(size=18), legend.text = element_text(size=16))

visual_ansh_plot_st1_gr <- ggplot(ansh_sum_st1_gr,aes(x=factor(Condition, level=c("Pre-Language", "Greek")), color=Color))+ 
  geom_boxplot(aes(middle=AbsoluteNo,lower=AbsoluteNo-se,upper=AbsoluteNo+se,ymin=AbsoluteNo-sd,ymax=AbsoluteNo+sd),stat="identity") +
  scale_color_manual(breaks = c("Blue", "Green"),values=c("blue", "darkgreen")) + ylim(-2, 30) + labs(y="", x ="") +
  stat_pvalue_manual(data = pairwise_visual_pre_gr[pairwise_visual_pre_gr$Neuron_Type == 'Shared',], label = "p.adj.signif", xmin = "group1", xmax="group2",y.position = c(0,20), color="Color", tip.length = 0, label.size = 8) +
  ggtitle("") +
  theme(plot.title = element_text(size = 21, hjust = 0.5), axis.text=element_text(size=18, color ="black"), legend.position="top", legend.key.size = unit(0.7, 'cm'), legend.title = element_text(size=18), legend.text = element_text(size=16))

visual_ansh_plot_st1_en_gr <- grid.arrange(visual_ansh_plot_st1_en, visual_ansh_plot_st1_gr, ncol=2)
ggsave(visual_ansh_plot_st1_en_gr, file=file.path("ANOVA",paste0("visual_shared_boxplot.png")))
```
# UNIQUE NEURONS (VISUAL AREAS): BOXPLOT
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pre_en_visual_unique <- pre_en_visual %>% filter(Neuron_Type %in% c("Unique"))
pre_gr_visual_unique <- pre_gr_visual %>% filter(Neuron_Type %in% c("Unique"))
anun_sum_st1_en <- summarySE(pre_en_visual_unique, measurevar="AbsoluteNo", groupvars=c("Color","Condition"))
anun_sum_st1_gr <- summarySE(pre_gr_visual_unique, measurevar="AbsoluteNo", groupvars=c("Color","Condition"))

visual_anun_plot_st1_en <- ggplot(anun_sum_st1_en,aes(x=factor(Condition, level=c("Pre-Language", "English")), color=Color))+ 
  geom_boxplot(aes(middle=AbsoluteNo,lower=AbsoluteNo-se,upper=AbsoluteNo+se,ymin=AbsoluteNo-sd,ymax=AbsoluteNo+sd),stat="identity") +
  scale_color_manual(breaks = c("Blue", "Green"),values=c("blue", "darkgreen")) + ylim(0, 32) + labs(y="", x ="") +
  stat_pvalue_manual(data = pairwise_visual_pre_en[pairwise_visual_pre_en$Neuron_Type == 'Unique',], label = "p.adj.signif", xmin = "group1", xmax="group2",y.position = c(30,20), color="Color", tip.length = 0, label.size = 8) +
  ggtitle("Visual areas (unique)") +
  theme(plot.title = element_text(size = 21, hjust = 0.5), axis.text=element_text(size=18, color ="black"), legend.position="top", legend.key.size = unit(0.7, 'cm'), legend.title = element_text(size=18), legend.text = element_text(size=16))

visual_anun_plot_st1_gr <- ggplot(anun_sum_st1_gr,aes(x=factor(Condition, level=c("Pre-Language", "Greek")), color=Color))+ 
  geom_boxplot(aes(middle=AbsoluteNo,lower=AbsoluteNo-se,upper=AbsoluteNo+se,ymin=AbsoluteNo-sd,ymax=AbsoluteNo+sd),stat="identity") +
  scale_color_manual(breaks = c("Blue", "Green"),values=c("blue", "darkgreen")) + ylim(0, 32) + labs(y="", x ="") +
  stat_pvalue_manual(data = pairwise_visual_pre_gr[pairwise_visual_pre_gr$Neuron_Type == 'Unique',], label = "p.adj.signif", xmin = "group1", xmax="group2",y.position = c(32,20), color="Color", tip.length = 0, label.size = 8) +
  ggtitle("") +
  theme(plot.title = element_text(size = 21, hjust = 0.5), axis.text=element_text(size=18, color ="black"), legend.position="top", legend.key.size = unit(0.7, 'cm'), legend.title = element_text(size=18), legend.text = element_text(size=16))

visual_anun_plot_st1_en_gr <- grid.arrange(visual_anun_plot_st1_en, visual_anun_plot_st1_gr, ncol=2)
ggsave(visual_anun_plot_st1_en_gr, file=file.path("ANOVA",paste0("visual_unique_boxplot.png")))
```

# VISUAL HUB (AT)
# PRE-LANGUAGE VS. ENGLISH (AT): ANOVA
```{r, echo=FALSE, message=FALSE, warning=FALSE}
anova_pre_en_at <- anova_test(data = pre_en_at, dv = AbsoluteNo, wid = Network, within = c(Condition,Neuron_Type,Color))
anova_pre_en_at <- as.data.frame(get_anova_table(anova_pre_en_at, correction = "GG"))
write.csv(anova_pre_en_at, file=file.path("ANOVA",paste0("visual_at_pre_en_anova.csv")))
anova_pre_en_at
```
# PRE-LANGUAGE VS. ENGLISH (AT): POST-HOC
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pairwise_at_pre_en <- pre_en_at %>% group_by(Neuron_Type, Color) %>% pairwise_t_test(AbsoluteNo ~ Condition, paired = TRUE)
write.csv(pairwise_at_pre_en, file=file.path("ANOVA",paste0("visual_at_pre_en_pairwise.csv")))
pairwise_at_pre_en
```
# PRE-LANGUAGE VS. GREEK (AT): ANOVA
```{r, echo=FALSE, message=FALSE, warning=FALSE}
anova_pre_gr_at <- anova_test(data = pre_gr_at, dv = AbsoluteNo, wid = Network, within = c(Condition,Neuron_Type,Color))
anova_pre_gr_at <- as.data.frame(get_anova_table(anova_pre_gr_at, correction = "GG"))
write.csv(anova_pre_gr_at, file=file.path("ANOVA",paste0("visual_at_pre_gr_anova.csv")))
anova_pre_gr_at
```
# PRE-LANGUAGE VS. GREEK (AT): POST-HOC
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pairwise_at_pre_gr <- pre_gr_at %>% group_by(Neuron_Type, Color) %>% pairwise_t_test(AbsoluteNo ~ Condition, paired = TRUE)
write.csv(pairwise_at_pre_gr, file=file.path("ANOVA",paste0("visual_at_pre_gr_pairwise.csv")))
pairwise_at_pre_gr
```
# SHARED NEURONS (AT): BOXPLOT
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pre_en_at_shared <- pre_en_at %>% filter(Neuron_Type %in% c("Shared"))
pre_gr_at_shared <- pre_gr_at %>% filter(Neuron_Type %in% c("Shared"))
ansh_sum_st1_en <- summarySE(pre_en_at_shared, measurevar="AbsoluteNo", groupvars=c("Color","Condition"))
ansh_sum_st1_gr <- summarySE(pre_gr_at_shared, measurevar="AbsoluteNo", groupvars=c("Color","Condition"))

at_ansh_plot_st1_en <- ggplot(ansh_sum_st1_en,aes(x=factor(Condition, level=c("Pre-Language", "English")), color=Color))+ 
  geom_boxplot(aes(middle=AbsoluteNo,lower=AbsoluteNo-se,upper=AbsoluteNo+se,ymin=AbsoluteNo-sd,ymax=AbsoluteNo+sd),stat="identity") +
  scale_color_manual(breaks = c("Blue", "Green"),values=c("blue", "darkgreen")) + ylim(-3, 30) + labs(y="", x ="") +
  stat_pvalue_manual(data = pairwise_at_pre_en[pairwise_at_pre_en$Neuron_Type == 'Shared',], label = "p.adj.signif", xmin = "group1", xmax="group2",y.position = c(-3,12), color="Color", tip.length = 0, label.size = 8) +
  ggtitle("Visual hub (AT), shared") +
  theme(plot.title = element_text(size = 21, hjust = 0.5), axis.text=element_text(size=18, color ="black"), legend.position="top", legend.key.size = unit(0.7, 'cm'), legend.title = element_text(size=18), legend.text = element_text(size=16))

at_ansh_plot_st1_gr <- ggplot(ansh_sum_st1_gr,aes(x=factor(Condition, level=c("Pre-Language", "Greek")), color=Color))+ 
  geom_boxplot(aes(middle=AbsoluteNo,lower=AbsoluteNo-se,upper=AbsoluteNo+se,ymin=AbsoluteNo-sd,ymax=AbsoluteNo+sd),stat="identity") +
  scale_color_manual(breaks = c("Blue", "Green"),values=c("blue", "darkgreen")) + ylim(-3, 30) + labs(y="", x ="") +
  stat_pvalue_manual(data = pairwise_at_pre_gr[pairwise_at_pre_gr$Neuron_Type == 'Shared',], label = "p.adj.signif", xmin = "group1", xmax="group2",y.position = c(-3,12), color="Color", tip.length = 0, label.size = 8) +
  ggtitle("") +
  theme(plot.title = element_text(size = 21, hjust = 0.5), axis.text=element_text(size=18, color ="black"), legend.position="top", legend.key.size = unit(0.7, 'cm'), legend.title = element_text(size=18), legend.text = element_text(size=16))

at_ansh_plot_st1_en_gr <- grid.arrange(at_ansh_plot_st1_en, at_ansh_plot_st1_gr, ncol=2)
ggsave(at_ansh_plot_st1_en_gr, file=file.path("ANOVA",paste0("visual_at_shared_boxplot.png")))
```
# UNIQUE NEURONS (AT): BOXPLOT
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pre_en_at_unique <- pre_en_at %>% filter(Neuron_Type %in% c("Unique"))
pre_gr_at_unique <- pre_gr_at %>% filter(Neuron_Type %in% c("Unique"))
anun_sum_st1_en <- summarySE(pre_en_at_unique, measurevar="AbsoluteNo", groupvars=c("Color","Condition"))
anun_sum_st1_gr <- summarySE(pre_gr_at_unique, measurevar="AbsoluteNo", groupvars=c("Color","Condition"))

at_anun_plot_st1_en <- ggplot(anun_sum_st1_en,aes(x=factor(Condition, level=c("Pre-Language", "English")), color=Color))+ 
  geom_boxplot(aes(middle=AbsoluteNo,lower=AbsoluteNo-se,upper=AbsoluteNo+se,ymin=AbsoluteNo-sd,ymax=AbsoluteNo+sd),stat="identity") +
  scale_color_manual(breaks = c("Blue", "Green"),values=c("blue", "darkgreen")) + ylim(0, 32) + labs(y="", x ="") +
  stat_pvalue_manual(data = pairwise_at_pre_en[pairwise_at_pre_en$Neuron_Type == 'Unique',], label = "p.adj.signif", xmin = "group1", xmax="group2",y.position = c(10,0), color="Color", tip.length = 0, label.size = 8) +
  ggtitle("Visual hub (AT), unique") +
  theme(plot.title = element_text(size = 21, hjust = 0.5), axis.text=element_text(size=18, color ="black"), legend.position="top", legend.key.size = unit(0.7, 'cm'), legend.title = element_text(size=18), legend.text = element_text(size=16))

at_anun_plot_st1_gr <- ggplot(anun_sum_st1_gr,aes(x=factor(Condition, level=c("Pre-Language", "Greek")), color=Color))+ 
  geom_boxplot(aes(middle=AbsoluteNo,lower=AbsoluteNo-se,upper=AbsoluteNo+se,ymin=AbsoluteNo-sd,ymax=AbsoluteNo+sd),stat="identity") +
  scale_color_manual(breaks = c("Blue", "Green"),values=c("blue", "darkgreen")) + ylim(0, 32) + labs(y="", x ="") +
  stat_pvalue_manual(data = pairwise_at_pre_gr[pairwise_at_pre_gr$Neuron_Type == 'Unique',], label = "p.adj.signif", xmin = "group1", xmax="group2",y.position = c(10,0), color="Color", tip.length = 0, label.size = 8) +
  ggtitle("") +
  theme(plot.title = element_text(size = 21, hjust = 0.5), axis.text=element_text(size=18, color ="black"), legend.position="top", legend.key.size = unit(0.7, 'cm'), legend.title = element_text(size=18), legend.text = element_text(size=16))

at_anun_plot_st1_en_gr <- grid.arrange(at_anun_plot_st1_en, at_anun_plot_st1_gr, ncol=2)
ggsave(at_anun_plot_st1_en_gr, file=file.path("ANOVA",paste0("visual_at_unique_boxplot.png")))
```

# SECONDARY VISUAL AREA (TO)
# PRE-LANGUAGE VS. ENGLISH (TO): ANOVA
```{r, echo=FALSE, message=FALSE, warning=FALSE}
anova_pre_en_to <- anova_test(data = pre_en_to, dv = AbsoluteNo, wid = Network, within = c(Condition,Neuron_Type,Color))
anova_pre_en_to <- as.data.frame(get_anova_table(anova_pre_en_to, correction = "GG"))
write.csv(anova_pre_en_to, file=file.path("ANOVA",paste0("visual_to_pre_en_anova.csv")))
anova_pre_en_to
```
# PRE-LANGUAGE VS. ENGLISH (TO): POST-HOC
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pairwise_to_pre_en <- pre_en_to %>% group_by(Neuron_Type, Color) %>% pairwise_t_test(AbsoluteNo ~ Condition, paired = TRUE)
write.csv(pairwise_to_pre_en, file=file.path("ANOVA",paste0("visual_to_pre_en_pairwise.csv")))
pairwise_to_pre_en
```
# PRE-LANGUAGE VS. GREEK (TO): ANOVA
```{r, echo=FALSE, message=FALSE, warning=FALSE}
anova_pre_gr_to <- anova_test(data = pre_gr_to, dv = AbsoluteNo, wid = Network, within = c(Condition,Neuron_Type,Color))
anova_pre_gr_to <- as.data.frame(get_anova_table(anova_pre_gr_to, correction = "GG"))
write.csv(anova_pre_gr_to, file=file.path("ANOVA",paste0("visual_to_pre_gr_anova.csv")))
anova_pre_gr_to
```
# PRE-LANGUAGE VS. GREEK (TO): POST-HOC
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pairwise_to_pre_gr <- pre_gr_to %>% group_by(Neuron_Type, Color) %>% pairwise_t_test(AbsoluteNo ~ Condition, paired = TRUE)
write.csv(pairwise_to_pre_gr, file=file.path("ANOVA",paste0("visual_to_pre_gr_pairwise.csv")))
pairwise_to_pre_gr
```
# SHARED NEURONS (TO): BOXPLOT
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pre_en_to_shared <- pre_en_to %>% filter(Neuron_Type %in% c("Shared"))
pre_gr_to_shared <- pre_gr_to %>% filter(Neuron_Type %in% c("Shared"))
ansh_sum_st1_en <- summarySE(pre_en_to_shared, measurevar="AbsoluteNo", groupvars=c("Color","Condition"))
ansh_sum_st1_gr <- summarySE(pre_gr_to_shared, measurevar="AbsoluteNo", groupvars=c("Color","Condition"))

to_ansh_plot_st1_en <- ggplot(ansh_sum_st1_en,aes(x=factor(Condition, level=c("Pre-Language", "English")), color=Color))+ 
  geom_boxplot(aes(middle=AbsoluteNo,lower=AbsoluteNo-se,upper=AbsoluteNo+se,ymin=AbsoluteNo-sd,ymax=AbsoluteNo+sd),stat="identity") +
  scale_color_manual(breaks = c("Blue", "Green"),values=c("blue", "darkgreen")) + ylim(-3, 30) + labs(y="", x ="") +
  stat_pvalue_manual(data = pairwise_to_pre_en[pairwise_to_pre_en$Neuron_Type == 'Shared',], label = "p.adj.signif", xmin = "group1", xmax="group2",y.position = c(-3,12), color="Color", tip.length = 0, label.size = 8) +
  ggtitle("Secondary visual area (TO), shared") +
  theme(plot.title = element_text(size = 21, hjust = 0.5), axis.text=element_text(size=18, color ="black"), legend.position="top", legend.key.size = unit(0.7, 'cm'), legend.title = element_text(size=18), legend.text = element_text(size=16))

to_ansh_plot_st1_gr <- ggplot(ansh_sum_st1_gr,aes(x=factor(Condition, level=c("Pre-Language", "Greek")), color=Color))+ 
  geom_boxplot(aes(middle=AbsoluteNo,lower=AbsoluteNo-se,upper=AbsoluteNo+se,ymin=AbsoluteNo-sd,ymax=AbsoluteNo+sd),stat="identity") +
  scale_color_manual(breaks = c("Blue", "Green"),values=c("blue", "darkgreen")) + ylim(-3, 30) + labs(y="", x ="") +
  stat_pvalue_manual(data = pairwise_to_pre_gr[pairwise_to_pre_gr$Neuron_Type == 'Shared',], label = "p.adj.signif", xmin = "group1", xmax="group2",y.position = c(-3,12), color="Color", tip.length = 0, label.size = 8) +
  ggtitle("") +
  theme(plot.title = element_text(size = 21, hjust = 0.5), axis.text=element_text(size=18, color ="black"), legend.position="top", legend.key.size = unit(0.7, 'cm'), legend.title = element_text(size=18), legend.text = element_text(size=16))

to_ansh_plot_st1_en_gr <- grid.arrange(to_ansh_plot_st1_en, to_ansh_plot_st1_gr, ncol=2)
ggsave(to_ansh_plot_st1_en_gr, file=file.path("ANOVA",paste0("visual_to_shared_boxplot.png")))
```
# UNIQUE NEURONS (TO): BOXPLOT
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pre_en_to_unique <- pre_en_to %>% filter(Neuron_Type %in% c("Unique"))
pre_gr_to_unique <- pre_gr_to %>% filter(Neuron_Type %in% c("Unique"))
anun_sum_st1_en <- summarySE(pre_en_to_unique, measurevar="AbsoluteNo", groupvars=c("Color","Condition"))
anun_sum_st1_gr <- summarySE(pre_gr_to_unique, measurevar="AbsoluteNo", groupvars=c("Color","Condition"))

to_anun_plot_st1_en <- ggplot(anun_sum_st1_en,aes(x=factor(Condition, level=c("Pre-Language", "English")), color=Color))+ 
  geom_boxplot(aes(middle=AbsoluteNo,lower=AbsoluteNo-se,upper=AbsoluteNo+se,ymin=AbsoluteNo-sd,ymax=AbsoluteNo+sd),stat="identity") +
  scale_color_manual(breaks = c("Blue", "Green"),values=c("blue", "darkgreen")) + ylim(0, 32) + labs(y="", x ="") +
  stat_pvalue_manual(data = pairwise_to_pre_en[pairwise_to_pre_en$Neuron_Type == 'Unique',], label = "p.adj.signif", xmin = "group1", xmax="group2",y.position = c(10,0), color="Color", tip.length = 0, label.size = 8) +
  ggtitle("Secondary visual area (TO), unique") +
  theme(plot.title = element_text(size = 21, hjust = 0.5), axis.text=element_text(size=18, color ="black"), legend.position="top", legend.key.size = unit(0.7, 'cm'), legend.title = element_text(size=18), legend.text = element_text(size=16))

to_anun_plot_st1_gr <- ggplot(anun_sum_st1_gr,aes(x=factor(Condition, level=c("Pre-Language", "Greek")), color=Color))+ 
  geom_boxplot(aes(middle=AbsoluteNo,lower=AbsoluteNo-se,upper=AbsoluteNo+se,ymin=AbsoluteNo-sd,ymax=AbsoluteNo+sd),stat="identity") +
  scale_color_manual(breaks = c("Blue", "Green"),values=c("blue", "darkgreen")) + ylim(0, 32) + labs(y="", x ="") +
  stat_pvalue_manual(data = pairwise_to_pre_gr[pairwise_to_pre_gr$Neuron_Type == 'Unique',], label = "p.adj.signif", xmin = "group1", xmax="group2",y.position = c(10,0), color="Color", tip.length = 0, label.size = 8) +
  ggtitle("") +
  theme(plot.title = element_text(size = 21, hjust = 0.5), axis.text=element_text(size=18, color ="black"), legend.position="top", legend.key.size = unit(0.7, 'cm'), legend.title = element_text(size=18), legend.text = element_text(size=16))

to_anun_plot_st1_en_gr <- grid.arrange(to_anun_plot_st1_en, to_anun_plot_st1_gr, ncol=2)
ggsave(to_anun_plot_st1_en_gr, file=file.path("ANOVA",paste0("visual_to_unique_boxplot.png")))
```

